---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Data and Code for NCS - SDG analysis"
```

# Link bewteen Natural Climate Solutions and Sustainable Development Goals

This repository contains the data and codes used to obtain results of the paper by Mariani et al. (202?) - Hit two targets with one stone with Natural Climate Solutions.

## Contents

[:file_folder: **rawdata**](rawdata/) directory contains the 0/1 matrix used to perform all analysis. See Material & Methods section of the paper for more details. This directory also contains SDG's and NCS's icons use in the figures of the paper. 

[:file_folder: **results**](results/) directory contains all `.RData` files generated during the analyses.

[:file_folder: **R**](R/) directory contains the functions used to perform all the analyses. It contains 4 `.R` files:

1. [:open_book: read_data.R](R/read_data.R) contains functions to read data. 
2. [:package: format_data.R](R/format_data.R) contains functions to format the data in the desired format to make the analyses and figures.
3. [:microscope: analysis.R](R/analysis.R) contains functions to perform analysis, mainly null models and correspondance. analysis. 
4. [:bar_chart: plot_data.R](R/plot_data.R) contains all functions to obtain plots in the paper.

[:file_folder: **figures**](figures/) directory contains all figures in the paper.

The [:hammer: dev_history.R](dev_history.R) file allow to rebuild our research compendium from scratch.

The [:briefcase: make.R](make.R) file allow to produce all the analyses and render the corresponding plots.

## How to run it?

This research compendium has been developed using the statistical programming language R. To work with the compendium, you will need installed on your computer the following softwares:

* R: [https://cloud.r-project.org/](https://cloud.r-project.org/) 
* RStudio: [https://rstudio.com/products/rstudio/download/](https://rstudio.com/products/rstudio/download/)
* Git: [https://git-scm.com/](https://git-scm.com/)
* Create a GitHub account: [https://github.com/](https://github.com/)

You can download the compendium by cloning this [repository](https://github.com/GaelMariani/NCSSDGproj). You can follow this [tutorial](https://resources.github.com/whitepapers/github-and-rstudio/#:~:text=Clone%20the%20repository%20with%20RStudio&text=Click%20the%20Copy%20to%20clipboard,the%20Project%20directory%20name%20field.), section **"Clone the repository with RStudio"** to clone the repository. <br>

Once the compendium is cloned, follow these steps:

  1. open the `.Rproj` file in RStudio.
  2. open [make.R](make.R) and run it to produce all the analyses.
  
Note that R version 3.6.2 or later is required. Run this command `utils::sessionInfo()` to check your R version. <br> You can uptade your R version [here](https://cran.r-project.org).
  
  
### Session Info
```{r}
utils::sessionInfo()
```

  
### Licenses
**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

**Data:** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse


