---
title: "Killing two birds with one stone with Natural Climate Solutions"
author: "Gael Mariani"
date: "`r Sys.Date()`"
bibliography: 
link-citations: true
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Targeted journal: Nature Climate Change*

Authors : Gaël Mariani, Fabien Moullec, ... Nicolas Loiseau, Marc Troussellier, David Mouillot

## Introduction

In 2015, the world’s leaders pledged to accomplish two of the greatest challenges that are facing humanity today. On the one hand, UN member countries adopted the 2030 Agenda for Sustainable Development, a comprehensive plan of action for “people, planet and prosperity”, featuring 17 Sustainable Development Goals (SDGs) and 169 targets1. On the other hand, the Paris Agreement on Climate Change intended to limit global warming below 2°C relative to preindustrial levels, and even pursuing the effort to further limit warming to 1.5°C2.
	With the exception of the one-off decrease in CO2 emissions related to the COVID-19 crisis in 20203, total CO2 emissions were still rising by around 1.5% per year in the last decade4,5, reducing the time left for action by two-thirds (Höhne et al. 2020). To shift to a pathway consistent with 2°C of global warming, the world’s countries have to drastically cut their CO2 emissions, while removing large amounts of CO2 from the atmosphere. The use of emerging technologies for carbon dioxide removal such as Bioenergy with Carbon Capture and Storage (BECCS) or Direct Air Carbon Capture and Storage (DACCS), are one of the most likely methods to realise negative emissions6,7 (Fuhrman et al. (2020)). In addition, Natural Climate Solutions (NCS) are now recognized as major opportunity for meeting Paris Agreement. These NCS promote carbon sequestration and/or reduce FINALEMENT TU PARLES SURTOUT DE SEQUESTRATION ENSUITE DONC POURQUOI NE PAS ENLEVER REDUCE CO2 emissions by conserving and restoring ecosystems or improving land management. Such measures could avoid the destruction of irrecoverable carbon stocks and may contribute up to 37% of the cost-effective mitigation (i.e. ≤US$100 per tonne of CO2e) needed by 20308,9. In comparison to emerging negative emissions technologies, NCS also provide a wide range of ecosystem services (or co-benefits) that can promote the achievement of several SDGs8,10. For example, mangroves improve coastal defence against extreme climate related events11, while forests promote water infiltration, thereby reducing the strength of flooding events12. Thus, by promoting carbon sequestration while providing several ecosystem services, NCS have the potential to both mitigate and adapt to climate change, but also promote the achievement of SDGs and their targets. This make them a useful tool for a sustainable future. 
Yet, the extent to which most of SDG targets have links with NCS and whether NCS can be complementary in their coverage of SDG targets are still unknown. Ultimately, identifying such relationships (synergies and trade-offs) between NCS and SDG targets, while assessing the structure of this bipartite network is now of particular importance13 and will provide key levers to policy-makers. 
	Here, we review the relationships (synergies and trade-offs) between NCS measures  that conserve, restore or manage sustainably ecosystems that sequester carbon over large time scale (Table 1), and SDG targets. We consider 11 ecosystems that can be divided into 3 groups: terrestrial ecosystems (forests, peatland, urban forests and grassland); coastal ecosystems (mangroves, saltmarshes, seagrasses, macroalgae); oceanic ecosystems (pelagic, mesopelagic and polar marine areas, and deep-sea sediment). To assess the interlinkage between these 11 ecosystems and the 169 targets (Figure 1), we use a consensus-based expert elicitation method and review the scientific literature to answer the following question: does the implementation of a given NCS promotes (or prevents) the achievement of a given target? 



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
